Probability

### 2016-04-09 prob.tex
prob.tex Fix a bug about the location of BibTeX...
prob.tex "Example 6. [Quantum probability measure]" update

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}(\{LLR\}) & = & 0\\
\mathbb{P}(\{LRL\}) & = & 0\\
\mathbb{P}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RLL\}) & = & 0\\
\mathbb{P}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}(\{RRR\}) & = & 0\\
\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the probability
of each electron is not independent~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction},
i.e., we cannot find three probability space for each subsystem such
that 
\[
\mathbb{P}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
\]
Correlated variables are also common in the classical world. For example,
if the first coin is head or tail decided by whether the temperature
is higher than a particular degree and the second coin is decided
by whether Coca Cola is sold more than a particular amount, then we
know these two coins are correlated. Einstein, Podolsky, and Rosen~\cite{EPR1935}
suggested any correlated quantum probability results may be interpreted
classically. For example, maybe the natural actually rolls an tetrahedron
die with $\{LLL,LRR,RLR,RRL\}$ in its four faces, and this tetrahedron
die could not be accessed by human for some reasons so that we think
we are handling three electrons.

The interesting part is that three electrons cannot be measured the
spin only along the $x$ axis, but also along the $y$ axis with the
result down ($D$) or up ($U$).

>>>>

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the probability
of each electron is not independent~\cite{GrahamKnuthPatashnik1994,inun.425605319950101,rohatgi2011introduction},
i.e., we cannot find three probability space for each subsystem such
that 
\[
\mathbb{P}_{xxx}(\{abc\})=\mathbb{P}(\{a\})\mathbb{P}(\{b\})\mathbb{P}(\{c\})\textrm{ .}
\]
Correlated variables are also common in the classical world. For example,
if the first coin is head or tail decided by whether the temperature
is higher than a particular degree and the second coin is decided
by whether Coca Cola is sold more than a particular amount, then we
know these two coins are correlated. Einstein, Podolsky, and Rosen
(EPR)~\cite{EPR1935} suggested any correlated quantum probability
results may be interpreted classically. For example, maybe the nature
actually rolls an tetrahedron die with $\{LLL,LRR,RLR,RRL\}$ in its
four faces, and this tetrahedron die could not be accessed by human
for some reasons so that we think we are handling three electrons.

In order to verify EPR's idea, we need to analysis the idea of probability
more carefully. Imagining somebody tosses a coin behind a veil, we
heard the coin is tossed, but cannot see the result. Although the
probability for us is still $\mathbb{P}(\{H\})=\mathbb{P}(\{T\})=\frac{1}{2}$,
we know the coin behind the veil must be either head or tail face-up.

In classical probability, there is no difference between the coins
have not been tossed or the coins have been tossed but we do not know.
However, there is a difference when we consider the quantum probability.
Because the three electrons can be specially separated, and each electron
can be measured along the $x$ axis separately, if the nature actually
rolled the tetrahedron die, this die should be rolled before the electrons
are separated and measured. In another word, there should be a period
that the human observer would not know the measurement results for
each electron along the $x$ axis, but the nature should know. The
result for $j$-th electron is denoted by $w\left(\sigma_{x}^{j}\right)$
so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
and $w\left(\sigma_{x}^{3}\right)$ must be odd.

The interesting part is that three electrons cannot be measured the
spin only along the $x$ axis, but also along the $y$ axis with the
result down ($D$) or up ($U$). We only consider to measure even
number of electrons along the $y$ axis, and the measure of non-singleton
set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
\begin{eqnarray*}
\begin{array}{rcl}
\mathbb{P}_{xyy}(\{LDD\}) & = & 0\\
\mathbb{P}_{xyy}(\{LDU\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RDD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{RDU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUD\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yxy}(\{DLD\}) & = & 0\\
\mathbb{P}_{yxy}(\{DLU\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRU\}) & = & 0\\
\mathbb{P}_{yxy}(\{ULD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{ULU\}) & = & 0\\
\mathbb{P}_{yxy}(\{URD\}) & = & 0\\
\mathbb{P}_{yxy}(\{URU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yyx}(\{DDL\}) & = & 0\\
\mathbb{P}_{yyx}(\{DDR\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UDL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{UDR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUL\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUR\}) & = & \frac{1}{4}
\end{array}
\end{eqnarray*}
Similarly, there would be predetermined $w\left(\sigma_{x}^{j}\right)$
and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Notice
that the nature should predetermine the same values of $w\left(\sigma_{x}^{j}\right)$
and $w\left(\sigma_{y}^{j}\right)$ no matter we measure along $x$
axes or $y$ axes because the nature does not know which axes we are
going to measure.
